---
pagetitle: "Public parks in Trafford"
lang: "en-GB"
output: 
  html_document:
    css: styles.css
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)

library(crosstalk) ; library(tidyverse) ; library(sf) ; library(leaflet) ; library(leaflet.extras) ; library(reactable) ; library(shiny) ; library(htmlwidgets) ; library(htmltools)

# local authority boundary
sf <- st_read("local_authority.geojson", quiet = TRUE)

# parks
df <- read_csv("data/parks.csv") %>% 
  mutate(website = ifelse(is.na(website), "", str_c("<a href='", website, "'target='_blank'>", str_remove(website, "http://www.|https://www.|www.|http://|https://"), "</a>")),
         twitter = ifelse(is.na(twitter), "", str_c("<a href='https://twitter.com/", twitter, "' target='_blank'>@", twitter, "</a>")),
         green_flag = ifelse(is.na(green_flag), "", str_c("<a href='", green_flag, "'target='_blank'>Green Flag Award Winner 2019/20</a>")),
         popup = ifelse(is.na(green_flag), str_c("<strong>", name, "</strong>") %>% map(HTML), str_c("<strong>", name, "</strong><br/>", green_flag) %>% map(HTML)))

# shared dataframe
sd <- SharedData$new(df, group = "name")
# subset of shared dataframe
sd_table <- select(df, name, website, twitter) %>%
  SharedData$new(group = "name")
```

```{r, map}
map <- leaflet(sd, width = "100%", height = 350) %>%
  addTiles(urlTemplate = "https://{s}.basemaps.cartocdn.com/light_all/{z}/{x}/{y}{r}.png", attribution = '&copy; <a href="https://www.openstreetmap.org/copyright">OpenStreetMap</a> contributors &copy; <a href="https://carto.com/attributions">CARTO</a> | <a href="https://www.ons.gov.uk/methodology/geography/licences">Contains OS data © Crown copyright and database right (2020)</a>', options = tileOptions(minZoom = 11, maxZoom = 18)) %>%
  addPolygons(data = sf, fillColor = "#CCCCCC", weight = 0.8, opacity = 1, color = "#212121") %>%  
  addAwesomeMarkers(popup = df$popup, icon = ~makeAwesomeIcon(icon = "tree-deciduous", library = "glyphicon", iconColor = "#006d2c", markerColor = "lightgreen")) %>%
  addEasyButton(
    easyButton(
      position = "topleft",
      icon = "fa-crosshairs",
      title = "Locate me",
      onClick = JS(c("function(btn,  map){map.locate({setView:true,enableHighAccuracy: true })}")))) %>% 
  onRender(paste0("function(el, x) {$('head').append(","\'<meta name=\"viewport\" content=\"width=device-width, initial-scale=1.0\">\'",");}"))
```

```{r, table}
# improve accessibility
options(reactable.language = reactableLang(
  noData = "No parks found",
  pagePreviousLabel = "Previous page",
  pageNextLabel = "Next page"))

table <- reactable(
  sd_table,
  columns = list(
    name = colDef(name = "Park"),
    website = colDef(name = "Website", html = TRUE),
    twitter = colDef(name = "Twitter", html = TRUE)),
  compact = TRUE,
  borderless = TRUE,
  sortable = FALSE,
  wrap = FALSE,
  highlight = TRUE,
  selection = "multiple",
  onClick = "select",
  rowStyle = list(cursor = "pointer")
)
```
<header>
```{r, logo}
a(
  href = "https://www.trafforddatalab.io", 
  img(src = "https://www.trafforddatalab.io/assets/logo/trafforddatalab_logo.svg", 
      alt = "Trafford Data Lab", 
      width = "100",
      style = "position:absolute; top:0; right:0; padding: 10px;")
  )
```
</header><main>
```{r, ui}
div(class = "container-fluid",
  div(class = "row",
      h1("Public parks in Trafford", style = "padding-top: 25px; margin-bottom: 20px;"),
      div(class = "col-xs-12 col-sm-6 col-md-6 col-lg-6", map),
      h2("Facilities", style = "margin-top: -3px;"),
      div(class = "col-xs-6 col-sm-3 col-md-3 col-lg-3", 
          list(
            # Playground
            filter_checkbox(id = "playground", label = NULL, sharedData = sd, group = ~ifelse(playground == 1, "Playground", NA), inline = TRUE),
            # Cafe
            filter_checkbox(id = "cafe", label = NULL, sharedData = sd, group = ~ifelse(cafe == 1, "Cafe", NA), inline = TRUE),
            # Toilets
            filter_checkbox(id = "toilets", label = NULL, sharedData = sd, group = ~ifelse(toilets == 1, "Toilets", NA), inline = TRUE),
            # Accessible toilets
            filter_checkbox(id = "accessible_toilet", label = NULL, sharedData = sd, group = ~ifelse(accessible_toilet == 1, "Accessible toilet", NA), inline = TRUE),
            # Pets' corner
            filter_checkbox(id = "pets_corner", label = NULL, sharedData = sd, group = ~ifelse(pets_corner == 1, "Pets' corner", NA), inline = TRUE),
            # Miniature railway
            filter_checkbox(id = "miniature_railway", label = NULL, sharedData = sd, group = ~ifelse(miniature_railway == 1, "Miniature railway", NA), inline = TRUE),
            # Basketball
            filter_checkbox(id = "basketball", label = NULL, sharedData = sd, group = ~ifelse(basketball == 1, "Basketball", NA), inline = TRUE)
           )),
      div(class = "col-xs-6 col-sm-3 col-md-3 col-lg-3", 
          list(
            # Bowling green
            filter_checkbox(id = "bowling", label = NULL, sharedData = sd, group = ~ifelse(bowling == 1, "Bowling green", NA), inline = TRUE),
            # Tennis courts
            filter_checkbox(id = "tennis", label = NULL, sharedData = sd, group = ~ifelse(tennis == 1, "Tennis courts", NA), inline = TRUE),
            # Football
            filter_checkbox(id = "football", label = NULL, sharedData = sd, group = ~ifelse(football == 1, "Football pitches", NA), inline = TRUE),
            # Outdoor gym
            filter_checkbox(id = "outdoor_gym", label = NULL, sharedData = sd, group = ~ifelse(outdoor_gym == 1, "Outdoor gym", NA), inline = TRUE),
            # BMX track
            filter_checkbox(id = "bmx_track", label = NULL, sharedData = sd, group = ~ifelse(bmx_track == 1, "BMX track", NA), inline = TRUE)),
          # Skate park
          filter_checkbox(id = "skate_park", label = NULL, sharedData = sd, group = ~ifelse(skate_park == 1, "Skate park", NA), inline = TRUE))),
  br(),
  div(class = "row",
      h2("Friends' Groups"),
      div(class = "col-sm-12", table)),
  div(class = "row",
      div(class = "col-sm-12", 
          p("If you spot an error, or there is something you'd like adding, please contact us at", a("infotrafford@trafford.gov.uk", href = 'mailto:infotrafford@trafford.gov.uk')), 
          p("For more information about parks in Trafford, please visit", a("trafford.gov.uk/parks", href = 'https://www.trafford.gov.uk/parks', target = "_blank"))),
      br()
      )
  )
```
</main>
<script>
  // Remove label tags created by crosstalk for the checkboxes causing validation errors
  // Reason for the error is that the 'for' attribute isn't referencing an id of a form control
  // NOTE: the do while loop always references array index 0 because as the elements are removed from the DOM they are also removed from the array
 
  var arrEmptyLabels = document.getElementsByClassName('control-label');
  
  do {
    var parent = arrEmptyLabels[0].parentNode;
    parent.removeChild(arrEmptyLabels[0]);
  }
  while (arrEmptyLabels.length > 0);
</script>